---
title: "Assignment-1"
author: "va306"
date: "2/05/2023"
output: html_document
---


```{r}
## Import csv file from dataset
library(readr)
Bumpus_sparrows <- read_csv("C:/Users/vidhi/Downloads/Bumpus_sparrows.csv")
Bumpus_sparrows
sparr <- Bumpus_sparrows
sparr
```
## Survived Sparrow Matrix
```{r}
survived=subset(sparr,Survivorship=='S')
survived

# Removing the non-numeric values

survived_num = survived[,-1]
survived_num
```
## Colmeans Survivorship
colMeans(survived_num)

## Covariance Survivorship
```{r}
## Covariance Survivorship
cov(survived_num)
cods=cov(survived_num)
cods
```
## Inference for Covariance Survivorship
* The covariance between Alar_extent and Total_Length is the maximum in the matrix column i.e. 9.1. It is a positive covariance. As the total_length increases Alar_extent also increase.
* The covariance between the L_hemerous and L_keel_sternum is the least. The covariance is very close to 0 and it can be inferred that there might be no relationship between L_hemerous and L_keel_sternum.

## Corelation Survivorship
```{r}
## Correlation Survivorship
cor(survived_num)
```

## Inference for Correlation Survivorship
* The correlation is usually between -1 to 1. As seen from the matrix, we mostly have a positive correlation.
* The maximum correlation is between the l_humerous and Alar_extent of approx 0.74.The survival chance are strongly dependednt on these 2 variables.


## Non-Survived Sparrow Matrix

```{r}
N_survived=subset(sparr,Survivorship=='NS')
N_survived

### Removing the non-numeric values
N_survived[,-1]
N_survived_num = N_survived[,-1]
```
## Colmeans Survivorship
colMeans(N_survived_num)

## Covariance Non-Survivors
```{r}
cov_data=cov(N_survived_num)
cov_data
```

## Inference for Covariance Non-Survivors
*  We observe that the covariance is maximum between the Total_length and Alar_extent as we saw in the Survivorship too. Both variables must be increasing or decreasing to get a positive correlation.
* Also, the least covariance is between the l_beak head and l_humerous.It's almost 0 and there is a possiblity of there being no relation between these variables.
* From co-variance graph it can be inferred that Alar_extent plays an important role in deciding the Survivorship. The value is 32.55 for Non-Survivors and approximately 17.5 for Survivors. The Alar_extent should be smaller to survive.

## Corelation Non-Survivors
```{r}
cor(N_survived_num)
```
## Inference for Correlation Survivorship
* As all the values are positive, we can see there has no negative correlation.
* The maximum is the correlation between the variables l_humerous and l_beak_head. The value shows it's a strong positive correlation.It's contrary to the the variables relation in covariance matrix.
 


```{r}
# Extra material for inference
```




# CONCLUSION with Comparing Total length
```{r}
library(ggplot2)
ggplot(sparr,aes(x=Total_length, fill=Survivorship))+geom_bar()+theme_bw()+
labs(title='Comparison-Length')
```


#Inference from the Total_length graph:

* As the Total_length increases the chances of Sparrows Surviving is less as compared to birds with shorter length.

# CONCLUSION with Comparing Alar_extent
```{r}
ggplot(sparr,aes(y=Alar_extent, fill=Survivorship))+geom_boxplot()+
labs(title='Comparison')
```

#Inference from the Alar_extent graph:

* For Alar_extent, if the median is above 242, the chances of sparrows surviving is more.



